---
title: "Sentiment Analysis Prediction on XGboost Model
author: "HD"
date: "`r Sys.Date()`"
output: html_document
---


```{r}
collected_data <- read.csv("C:/MSBA 24/unstructur/collected_data_with_sentiment.csv", header = TRUE)

collected_data$CleanComments <- gsub("[[:punct:]]", "", collected_data$Comment)

#Split the cleaned comments into words and count 
collected_data$WordCount <- sapply(strsplit(collected_data$CleanComments, " +"), length)

```

Making a model to predict sentiment based on word count and rating and sentiment score because the sentiment score could only be strong or week but does not lean towards positive or negative, I am trying to reclassify the sentiment based on more results like word count and rating other than the previous sentiment from the sentiment analysis model. 

```{r}

library(caret)
set.seed(123) 

collected_data$BinarySentiment <- ifelse(collected_data$Sentiment == "POSITIVE", 1, 0)

index <- createDataPartition(collected_data$BinarySentiment, p = 0.8, list = FALSE)
train_data <- collected_data[index, ]
test_data <- collected_data[-index, ]

library(xgboost)

# Prepare training and testing matrices
train_matrix <- as.matrix(train_data[, c("WordCount", "Rating", "SentimentScore")])
test_matrix <- as.matrix(test_data[, c("WordCount", "Rating", "SentimentScore")])

dtrain <- xgb.DMatrix(data = train_matrix, label = train_data$BinarySentiment)
dtest <- xgb.DMatrix(data = test_matrix, label = test_data$BinarySentiment)



# Train the model
xgb_model <- xgboost(
    eta = 0.3,
    data = dtrain,
    nrounds = 100, 
    verbose = 1, 
    
)

# Predict on test data
pred_probs <- predict(xgb_model, dtest)
pred_labels <- ifelse(pred_probs > 0.5, 1, 0) # Convert probabilities to binary labels

# Generate confusion matrix
library(caret)
conf_matrix <- confusionMatrix(factor(pred_labels), factor(test_data$BinarySentiment))

print(conf_matrix)

```

There is 87.38% correct compare to the sentiment analysis model but I am not sure if it even matters because the analysis only get the sentiment from sentiment score.

```{r}
train_predictions <- predict(xgb_model, dtrain)
train_predicted_sentiment <- ifelse(train_predictions > 0.5, "POSITIVE", "NEGATIVE")

# Predicting sentiment for the test set
test_predictions <- predict(xgb_model, dtest)
test_predicted_sentiment <- ifelse(test_predictions > 0.5, "POSITIVE", "NEGATIVE")

# Combining predictions
combined_predictions <- character(nrow(collected_data))
combined_predictions[index] <- train_predicted_sentiment
combined_predictions[-index] <- test_predicted_sentiment

collected_data$NewSentiment <- combined_predictions

#compare the new sentiment with the old sentiment and grab out the different ones 
different_sentiment <- collected_data[collected_data$Sentiment != collected_data$NewSentiment, c("Comment", "Sentiment", "NewSentiment")]

```
I listed all the comment that has different sentiment from the old sentiment and the new sentiment. and compared between them. but i cant look into all 1300 of them to see if the new sentiment is better than the old sentiment. But from the ones I looked at the newsentiment got some right and some wrong still. 

